Reliable error estimation for Sobol' indices\thanks{This work is supported by the CITiES project funded by the Agence Nationale de la Recherche (grant ANR-12-MONU-0020) and by the United States National Science Foundation (grant DMS-1522687).}

### 2017-02-20 article_review/Manuscript.tex

\subsection{Extension to Sobol' indices}
\label{sec:3.2}
The idea here is to extend the definition of the error bound (\ref{errbd}) to Sobol' indices. To achieve this goal, we consider the two integral formulas of the first-order and total effect Sobol' indices with $|u|=1$:
%\subsection{Definition of $\widehat{S}$ (fix it with max and min)}
%In some applications, it is more useful to estimate the normalized Sobol' indices, $S_u = \underline{\tau}_u^2/\sigma^2$ and $\overline{S}_u = \overline{\tau}_u^2/\sigma^2$. In both cases, regular and normalized indices can be approximated by estimating some integrals,
{\color{purple}(Lolo)
\begin{align*}
\underline{S}_u(\vI) & = \frac{\int_{[0,1)^{2d}} \left(f(\vx_u:{\vx'}_{-u})-f(\vx')\right)f(\vx)d\vx d{\vx'}}{\int_{[0,1)^{d}} f(\vx)^2 d{\vx}-\left(\int_{[0,1)^{d}} f(\vx) d{\vx}\right)^2}, \\ 
\underline{S}_u(\vI) & = \frac{I_1}{I_3-(I_4)^2}, \\
\overline{S}_u(\vI) & = \frac{\frac{1}{2}\int_{[0,1)^{d+1}}(f(\vx')-f(\vx_u:{\vx'}_{-u}))^2d\vx_u d{\vx'}}{\int_{[0,1)^{d}} f(\vx)^2 d{\vx}-\left(\int_{[0,1)^{d}} f(\vx) d{\vx}\right)^2}, \\
\overline{S}_u(\vI) & = \frac{I_2}{I_3-(I_4)^2},
\end{align*}
}
where $\vI=(I_1,I_2,I_3,I_4)$ is a vector of integral values. Indices $\underline{S}_u(\vI)$ and $\overline{S}_u(\vI)$ are defined as functions over the vector $\vI$. If we estimate $\vI$ by $\widehat{\vI}$ with vector of error bounds $\varepsilon_{\widehat{\vI}}=(\epsilon_{\widehat{I}_1},\epsilon_{\widehat{I}_2},\epsilon_{\widehat{I}_3}$, $\epsilon_{\widehat{I}_4})$ according to (\ref{errbd}), we know that $\vI\in B_{\varepsilon_{\widehat{\vI}}}(\widehat{\vI})=[\widehat{\vI}-\varepsilon_{\widehat{\vI}},\widehat{\vI}+\varepsilon_{\widehat{\vI}} ]$.

Then, as an alternative to the common Sobol' indices estimators (\ref{common.sobol.est}), we can define the following two estimators with their respective error bounds:
\begin{gather}
\begin{aligned}
\widehat{\underline{S}}_u & = \frac{1}{2}\left(\min\Big{(}\max_{\vI\in B_{\varepsilon_{\widehat{\vI}}}(\widehat{\vI})} \underline{S}_u(\vI),1\Big{)} + \max\Big{(}\min_{\vI\in B_{\varepsilon_{\widehat{\vI}}}(\widehat{\vI})} \underline{S}_u(\vI),0\Big{)} \right) \\
\varepsilon_{\widehat{\underline{S}}_u} & = \frac{1}{2}\left(\min\Big{(}\max_{\vI\in B_{\varepsilon_{\widehat{\vI}}}(\widehat{\vI})} \underline{S}_u(\vI),1\Big{)} - \max\Big{(}\min_{\vI\in B_{\varepsilon_{\widehat{\vI}}}(\widehat{\vI})} \underline{S}_u(\vI),0\Big{)} \right)
\end{aligned}
\label{formula_undersu}
\end{gather}
and,
\begin{gather}
\begin{aligned}
\widehat{\overline{S}}_u & = \frac{1}{2}\left(\min\Big{(}\max_{\vI\in B_{\varepsilon_{\widehat{\vI}}}(\widehat{\vI})} \overline{S}_u(\vI),1\Big{)} + \max\Big{(}\min_{\vI\in B_{\varepsilon_{\widehat{\vI}}}(\widehat{\vI})} \overline{S}_u(\vI),0\Big{)} \right) \\
\varepsilon_{\widehat{\overline{S}}_u} & = \frac{1}{2}\left(\min\Big{(}\max_{\vI\in B_{\varepsilon_{\widehat{\vI}}}(\widehat{\vI})} \overline{S}_u(\vI),1\Big{)} - \max\Big{(}\min_{\vI\in B_{\varepsilon_{\widehat{\vI}}}(\widehat{\vI})} \overline{S}_u(\vI),0\Big{)} \right)
\end{aligned}
\label{formula_oversu}
\end{gather}
Because numerator and denominator are both known to be positive, maximizing $\underline{S}_u(\vI)$ (resp. $\overline{S}_u(\vI)$) is done through maximizing the numerator $I_1$ (resp. $I_2$) and minimizing the denominator $I_3-I_4^2$. Analogously, to minimize $\underline{S}_u(\vI)$ (resp. $\overline{S}_u(\vI)$) one minimizes the numerator $I_1$ (resp. $I_2$) and maximizes the denominator $I_3-I_4^2$. As an example, Figure \ref{fig:1} illustrates the region of possible values of $\underline{S}_2(\vI)$ given the true value of $I_1$ for the test function of Bratley \textit{et al.} \cite{Bratley}. This function is further described in Section \ref{sec:5}. 
\begin{figure}[t]
\caption{The delimited region on the figure represents the values $\underline{S}_2$ in $\vI\in B_{(0,0,0.05,0.1)}(\widehat{\vI})$ for the Bratley \textit{et al.} function. There, $\underline{S}_2^{\min}=\max\Big{(}\min_{\vI\in B_{\varepsilon_{\vI}}(\widehat{\vI})} \underline{S}_2(\vI),0\Big{)}$ and $\underline{S}_2^{\max}=\min\Big{(}\max_{\vI\in B_{\varepsilon_{\vI}}(\widehat{\vI})} \underline{S}_2(\vI),1\Big{)}$, and $\widehat{\underline{S}}_2=(\underline{S}_2^{\min}+\underline{S}_2^{\max})/2$.}
\centering
\includegraphics[width=.5\textwidth]{estimator_3d_small.eps}
\label{fig:1}       % Give a unique label
\end{figure}

Under the assumption that each integrand in $\underline{S}_u$ and $\overline{S}_u$ lies inside $\cc$, these new estimators satisfy: \[ \underline{S}_u\in \left[ \widehat{\underline{S}}_u - \varepsilon_{\widehat{\underline{S}}_u}, \widehat{\underline{S}}_u + \varepsilon_{\widehat{\underline{S}}_u} \right], \qquad \overline{S}_u\in \left[ \widehat{\overline{S}}_u - \varepsilon_{\widehat{\overline{S}}_u}, \widehat{\overline{S}}_u + \varepsilon_{\widehat{\overline{S}}_u} \right] .\]
\comment{Because we do not assume the knowledge of the Walsh coefficients, it is hard to verify whether all the integrands lie in $\cc$. Nevertheless, some data-based necessary conditions are provided in \cite{HicJimLi}. These conditions can be used to automatically enlarge the cone according to each integrand.} For the rest of the article, we will consider $\widehat{\underline{S}}_u$ and $\widehat{\overline{S}}_u$ as defined in formulas (\ref{formula_undersu}) and (\ref{formula_oversu}).

@@

\begin{figure}[!ht]
\caption{Boxplots of estimation errors $\delta_{\underline{S}_u}$ obtained with both Variant $A.b$ and the random sampling method. The dashed horizontal line marks the tolerance $\varepsilon=5\cdot 10^{-3}$.}
\centering
\vspace*{0.2cm}
\includegraphics[width=0.4\textwidth]{comp_MC_first.eps}
\label{compa_MC_first}
\end{figure}

\begin{figure}[!ht]
\caption{Boxplots of estimation errors $\delta_{\overline{S}_u}$ obtained with both Variant $A.b$ and the random sampling method. The dashed horizontal line marks the tolerance $\varepsilon=5\cdot 10^{-3}$.}
\centering
\vspace*{0.2cm}
\includegraphics[width=0.4\textwidth]{comp_MC_tot.eps}
\label{compa_MC_tot}
\end{figure}}

>>>>

\subsection{Extension to Sobol' indices}
\label{sec:3.2}
In this section we will extend the definition of the error bound (\ref{errbd}) to Sobol' indices. To achieve this goal, we consider the two integral formulas of the first-order and total effect Sobol' indices with $|u|=1$:
%\subsection{Definition of $\widehat{S}$ (fix it with max and min)}
%In some applications, it is more useful to estimate the normalized Sobol' indices, $S_u = \underline{\tau}_u^2/\sigma^2$ and $\overline{S}_u = \overline{\tau}_u^2/\sigma^2$. In both cases, regular and normalized indices can be approximated by estimating some integrals,
{\color{purple}(Lolo)
\begin{align*}
\underline{S}_u(\vI) & = \frac{\int_{[0,1)^{2d}} \left(f(\vx_u:{\vx'}_{-u})-f(\vx')\right)f(\vx)d\vx d{\vx'}}{\int_{[0,1)^{d}} f(\vx)^2 d{\vx}-\left(\int_{[0,1)^{d}} f(\vx) d{\vx}\right)^2}, \\ 
\underline{S}_u(\vI) & = \frac{I_1}{I_3-(I_4)^2}, \\
\overline{S}_u(\vI) & = \frac{\frac{1}{2}\int_{[0,1)^{d+1}}(f(\vx')-f(\vx_u:{\vx'}_{-u}))^2d\vx_u d{\vx'}}{\int_{[0,1)^{d}} f(\vx)^2 d{\vx}-\left(\int_{[0,1)^{d}} f(\vx) d{\vx}\right)^2}, \\
\overline{S}_u(\vI) & = \frac{I_2}{I_3-(I_4)^2},
\end{align*}
}
where $\vI=(I_1,I_2,I_3,I_4)$ is a vector of integral values. Indices $\underline{S}_u(\vI)$ and $\overline{S}_u(\vI)$ are defined as functions over the vector $\vI$. If we estimate $\vI$ by $\widehat{\vI}$ with known error bounds $\varepsilon_{\widehat{\vI}}=(\epsilon_{\widehat{I}_1},\epsilon_{\widehat{I}_2},\epsilon_{\widehat{I}_3}$, $\epsilon_{\widehat{I}_4})$ according to (\ref{errbd}), we know that $\vI\in B_{\varepsilon_{\widehat{\vI}}}(\widehat{\vI})=[\widehat{\vI}-\varepsilon_{\widehat{\vI}},\widehat{\vI}+\varepsilon_{\widehat{\vI}} ]$.

Then, as an alternative to the common Sobol' indices estimators (\ref{common.sobol.est}), we can define the following two estimators with their respective error bounds:
\begin{gather}
\begin{aligned}
\widehat{\underline{S}}_u & = \frac{1}{2}\left(\min\Big{(}\max_{\vI\in B_{\varepsilon_{\widehat{\vI}}}(\widehat{\vI})} \underline{S}_u(\vI),1\Big{)} + \max\Big{(}\min_{\vI\in B_{\varepsilon_{\widehat{\vI}}}(\widehat{\vI})} \underline{S}_u(\vI),0\Big{)} \right) \\
\varepsilon_{\widehat{\underline{S}}_u} & = \frac{1}{2}\left(\min\Big{(}\max_{\vI\in B_{\varepsilon_{\widehat{\vI}}}(\widehat{\vI})} \underline{S}_u(\vI),1\Big{)} - \max\Big{(}\min_{\vI\in B_{\varepsilon_{\widehat{\vI}}}(\widehat{\vI})} \underline{S}_u(\vI),0\Big{)} \right)
\end{aligned}
\label{formula_undersu}
\end{gather}
and,
\begin{gather}
\begin{aligned}
\widehat{\overline{S}}_u & = \frac{1}{2}\left(\min\Big{(}\max_{\vI\in B_{\varepsilon_{\widehat{\vI}}}(\widehat{\vI})} \overline{S}_u(\vI),1\Big{)} + \max\Big{(}\min_{\vI\in B_{\varepsilon_{\widehat{\vI}}}(\widehat{\vI})} \overline{S}_u(\vI),0\Big{)} \right) \\
\varepsilon_{\widehat{\overline{S}}_u} & = \frac{1}{2}\left(\min\Big{(}\max_{\vI\in B_{\varepsilon_{\widehat{\vI}}}(\widehat{\vI})} \overline{S}_u(\vI),1\Big{)} - \max\Big{(}\min_{\vI\in B_{\varepsilon_{\widehat{\vI}}}(\widehat{\vI})} \overline{S}_u(\vI),0\Big{)} \right)
\end{aligned}
\label{formula_oversu}
\end{gather}
Because numerator and denominator are both known to be positive, maximizing $\underline{S}_u(\vI)$ (resp. $\overline{S}_u(\vI)$) is done through maximizing the numerator $I_1$ (resp. $I_2$) and minimizing the denominator $I_3-I_4^2$. Analogously, to minimize $\underline{S}_u(\vI)$ (resp. $\overline{S}_u(\vI)$) one minimizes the numerator $I_1$ (resp. $I_2$) and maximizes the denominator $I_3-I_4^2$. As an example, Figure \ref{fig:1} illustrates the region of possible values of $\underline{S}_2(\vI)$ given the true value of $I_1$ for the test function of Bratley \textit{et al.} \cite{Bratley}. This function is further described in Section \ref{sec:5}. 
\begin{figure}[t]
\caption{The delimited region in the figure represents the possible values of $\underline{S}_2$ for $\vI\in B_{(0,0,0.05,0.1)}(\widehat{\vI})$ (Bratley \textit{et al.} function). There, $\underline{S}_2^{\min}=\max\Big{(}\min_{\vI\in B_{\varepsilon_{\vI}}(\widehat{\vI})} \underline{S}_2(\vI),0\Big{)}$, $\underline{S}_2^{\max}=\min\Big{(}\max_{\vI\in B_{\varepsilon_{\vI}}(\widehat{\vI})} \underline{S}_2(\vI),1\Big{)}$, and $\widehat{\underline{S}}_2=(\underline{S}_2^{\min}+\underline{S}_2^{\max})/2$.}
\centering
\includegraphics[width=.5\textwidth]{estimator_3d_small.eps}
\label{fig:1}       % Give a unique label
\end{figure}

By construction, under the assumption that each integrand in $\underline{S}_u$ and $\overline{S}_u$ lies inside $\cc$, these new estimators satisfy: \[ \underline{S}_u\in \left[ \widehat{\underline{S}}_u - \varepsilon_{\widehat{\underline{S}}_u}, \widehat{\underline{S}}_u + \varepsilon_{\widehat{\underline{S}}_u} \right], \qquad \overline{S}_u\in \left[ \widehat{\overline{S}}_u - \varepsilon_{\widehat{\overline{S}}_u}, \widehat{\overline{S}}_u + \varepsilon_{\widehat{\overline{S}}_u} \right] .\]
\comment{Because we do not assume the knowledge of the Walsh coefficients, it is hard to verify whether all the integrands lie in $\cc$. Nevertheless, some data-based necessary conditions are provided in \cite{HicJimLi}. These conditions can be used to automatically enlarge the cone according to each integrand.} For the rest of the article, we will consider $\widehat{\underline{S}}_u$ and $\widehat{\overline{S}}_u$ as defined in formulas (\ref{formula_undersu}) and (\ref{formula_oversu}).

@@

\begin{figure}[!ht]
\caption{Boxplots of estimation errors $\delta_{\underline{S}_u}$ obtained with both Variant $A.b$ and the random sampling method. The dashed horizontal line marks the tolerance $\varepsilon=5\cdot 10^{-3}$.}
\centering
\vspace*{0.2cm}
\includegraphics[width=0.4\textwidth]{comp_mc_first.eps}
\label{compa_MC_first}
\end{figure}

\begin{figure}[!ht]
\caption{Boxplots of estimation errors $\delta_{\overline{S}_u}$ obtained with both Variant $A.b$ and the random sampling method. The dashed horizontal line marks the tolerance $\varepsilon=5\cdot 10^{-3}$.}
\centering
\vspace*{0.2cm}
\includegraphics[width=0.4\textwidth]{comp_mc_tot.eps}
\label{compa_MC_tot}
\end{figure}}

### 2017-02-20 article_review/reviewer_letter.tex

\textcolor{blue}{Dear associated editor and reviewers,\\
we would like to thank you for the positive and constructive feedback. Below we have compiled a detailed list of answers (blue text) to the issues raised in the review reports. In particular, in light of reviewer's two remark, the Asian option problem was replaced with a new ``real function''.\\
Best regards,\\
Laurent Gilquin and Llu\'{i}s Antoni Jim\'{e}nez Rugama}

@@

\textbf{\large{Reviewer $1$}}
\vspace*{0.5cm}

@@

\answer{As the reviewer claims, this is a key point that we revised and explained with more detail. It is really hard to verify whether an integrand satisfies the cone condition. Indeed, because we choose our mapping $\tilde{\vk}$ heuristically, the cone conditions will also depend on the scrambling. At the end of section 3 we cited some data-based necessary conditions that can help identify when integrands are not in the cone. In addition, also at the beginning of section 5, we noted that if the error bound is not satisfied it is certain that the integrand is not in the cone.}
\end{itemize}

@@

\textbf{\large{Reviewer $2$}}
\vspace*{0.5cm}

@@

\textbf{Minor comments}:
\begin{itemize}
\item[a.] page $2$ line $48$: it should be clear that $v \subset $u excludes $v = u$.

>>>>

\textcolor{blue}{Dear associated editor and reviewers,\\
we would like to thank you for the positive and constructive feedback. Below we have compiled a detailed list of answers (blue text) to the issues raised in the review reports. The corresponding modifications in the manuscript are colored in purple. In particular, in light of reviewer's two remark, the Asian option problem was replaced with a new application.\\
Best regards,\\
Laurent Gilquin and Llu\'{i}s Antoni Jim\'{e}nez Rugama}

@@

\newpage
\textbf{\large{Reviewer $1$}}
\vspace*{0.5cm}

@@

\answer{As the reviewer claims, this is a key point that we revised and explained with more detail. It is really hard to verify whether an integrand satisfies the cone condition. Indeed, because we choose our mapping $\tilde{\vk}$ heuristically, the cone conditions will also depend on the scrambling. At the end of section 3 we cited some data-based necessary conditions that can help identify when integrands are not in the cone. In addition, also at the beginning of section 5, we noted that if the error bound is not satisfied it is certain that the integrand is not in the cone.}
\end{itemize}
\vspace*{0.5cm}

@@

\newpage
\textbf{\large{Reviewer $2$}}
\vspace*{0.5cm}

@@

\newpage
\textbf{Minor comments}:
\begin{itemize}
\item[a.] page $2$ line $48$: it should be clear that $v \subset $u excludes $v = u$.
